### 2014-06-18 ms/ms.Rmd
simplify code for auhtor list
Remove ISSN records from bib files

# *Ecological Archives* Exxxxx
# Falster D.S. *et al* BAAD: a Biomass And Allometry Database for woody plants.*Ecology* xxxx

@@

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:**", lisOfAuthors(vardef=var.def)))
```

>>>>

# *Ecological Archives* Exxxxx
# Falster D.S. *et al* BAAD: a Biomass And Allometry Database for woody plants. *Ecology* xxxx

@@

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:**", lisOfAuthors(baad$contact)))
```
